\ifdefined\iscombined
	\lecturetitle{Code Coverage}
\else
\documentclass{article}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{mathtools}

\date{
	\vspace{-.75em}
	{\large \today}
}

\title{
	\vspace*{-1.5em}
	{\Huge Lecture 6} \\
	\vspace{-1em}
	\rule{\textwidth/4}{.01em} \\
	\vspace{-.25em}
	{\Large Code Coverage}
	\vspace{-.75em}
}

\author{
	{\large Matthew Farah}
}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
	citecolor=blue,
	anchorcolor=blue
}

\fancyhead{}
\fancyhead[L]{\today}
\fancyhead[R]{Lecture 6 - Code Coverage}

\sectionfont{\fontsize{12}{12}\bfseries}
\subsectionfont{\fontsize{10}{12}\normalfont}
\subsubsectionfont{\fontsize{10}{12}\normalfont}

\begin{document}

\maketitle
\pagestyle{fancy}

\fi

\begin{itemize}
	\item Bugs tend to cluster together in systems.
	\begin{itemize}
		\item Generally, 20\% of code is responsible for 80\% of bugs.
	\end{itemize}
	\item Tests can be `formal' or `informal'.
	\begin{itemize}
		\item Formal tests are done in a specific way and check specific things.
		\item Informal tests look at subjective things without a rigorous methodology.
	\end{itemize}
	\item Some examples of formal and informal tests are as follows:
	\begin{itemize}
		\item Exploratory testing.
		\begin{itemize}
			\item TLDR; Manually fucking around with the system and seeing what happens.
			\item Informal.
		\end{itemize}
		\item Fuzz testing.
		\begin{itemize}
			\item TLDR; Automated exploratory testing.
			\item Informal.
		\end{itemize}
		\item Model-based testing.
		\begin{itemize}
			\item TLDR; Creating formal models of the system to automatically generate tests.
			\item Formal.
		\end{itemize}
		\item Specifications-based testing.
		\begin{itemize}
			\item TLDR; Using invariants and pre/post-conditions of the system to test its behaviour.
			\item Formal.
		\end{itemize}
	\end{itemize}
	\item All tests are either:
	\begin{enumerate}
		\item Robust.
		\begin{itemize}
			\item Checks \underline{both} valid and invalid inputs.
		\end{itemize}
		\item Normal.
		\begin{itemize}
			\item Checks \underline{only} valid inputs.
		\end{itemize}
	\end{enumerate}
	\item As well, all tests are either:
	\begin{itemize}
		\item Strong.
		\begin{itemize}
			\item Makes no assumption about how many bugs the code can have.
		\end{itemize}
		\item Weak.
		\begin{itemize}
			\item Assumes the code being tested can only have one bug in it.
		\end{itemize}
	\end{itemize}
	\item Every test can be described as some combination of Robust/Normal and Strong/Weak.
	\item A program's Control Flow Graph (CFG) is a graph representing the sequence of instructions that can be executed by the program.
	\item A path is a sequence of valid execution steps in a CFG.
	\begin{itemize}
		\item Paths must start at a valid entry point of the program and end at some exit point.
	\end{itemize}
	\item A set of paths are said to be linearly independent if none of them can be expressed as some combination of the other paths in the set.
	\item A test suite's coverage is a measurement (metric) describing how much of the code is being tested.
	\begin{itemize}
		\item Coverage can be defined in multiple ways.
	\end{itemize}
	\item The five main definitions of test coverage are:
	\begin{enumerate}
		\item Statement/line coverage.
		\begin{itemize}
			\item Achieved when every line of code is tested.
		\end{itemize}
		\item Condition coverage.
		\begin{itemize}
			\item Achieved when every boolean of the code has been tested as true and false.
		\end{itemize}
		\item Branch/Decision coverage.
		\begin{itemize}
			\item Achieved when every possible branch in the code has been tested.
		\end{itemize}
		\item Modified Condition/Decision Coverage (MC/DC).
		\begin{itemize}
			\item Achieved when:
			\begin{enumerate}
				\item Every entry and exit point has been invoked.
				\item Every decision outcome has been tested.
				\item Each condition in a decision that can independently change the outcome of the decision has been tested.
			\end{enumerate}
		\end{itemize}
		\item Path coverage.
		\begin{itemize}
			\item Achieved when all possible linearly independent paths through the CFG have been tested.
		\end{itemize}
	\end{enumerate}
\end{itemize}

\ifdefined\iscombined
	\newpage
\else
	\end{document}
\fi
