\ifdefined\iscombined
	\lecturetitle{Verification}
\else
\documentclass{article}
\usepackage{changepage}
\usepackage{centernot}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{braket}
\usepackage{comment}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning}

\date{
	\vspace{-.75em}
	{\large \today}
}

\title{
	\vspace*{-1.5em}
	{\Huge Lecture 15} \\
	\vspace{-1em}
	\rule{\textwidth/4}{.01em} \\
	\vspace{-.25em}
	{\Large Verification}
	\vspace{-.75em}
}

\author{
	{\large Matthew Farah}
}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
	citecolor=blue,
	anchorcolor=blue
}

\fancyhead{}
\fancyhead[L]{\today}
\fancyhead[R]{Lecture 15 - Verification}

\setlength{\parindent}{0cm}

\lstset{
	basicstyle=\ttfamily\small,
	frame=single,
	tabsize=4,
	breaklines=true,
	numbers=left,
	numberstyle=\tiny,
	numbersep=8pt,
	xleftmargin=1.5em,
	framexleftmargin=1.5em
}

\newcounter{example}
\renewcommand{\theexample}{\arabic{example}}

\newenvironment{example}[1][]{
	\refstepcounter{example}
	\begin{adjustwidth}{1.5em}{}
	\noindent\textbf{\ifx&#1&Example \theexample:\else Example \theexample \ (#1):\fi}
	\ignorespaces
}{
	\vspace{.5em}
	\end{adjustwidth}
}

\newcounter{subexample}
\renewcommand{\thesubexample}{\alph{subexample}}

\newenvironment{subexample}{
	\setcounter{step}{0}
	\refstepcounter{subexample}
	\vspace{1em}\par\noindent
	\begin{adjustwidth}{1.5em}{}
	\noindent\textbf{(\thesubexample)}
	\ignorespaces
}{
	\par
	\vspace{1em}
	\end{adjustwidth}
}

\newenvironment{solution}{
	\vspace{.5em}
	\par
	\begin{adjustwidth}{1.5em}{}
	\textbf{{Solution:}}
	\par
	\vspace{.5em}
}{
	\vspace{1em}
	\end{adjustwidth}
}

\newcounter{step}
\renewcommand{\thestep}{\Roman{step}}

\newenvironment{step}{
	\refstepcounter{step}
	\vspace{1em}\par\noindent
	\ignorespaces\noindent\textbf{(\thestep)}
	\ignorespaces
}{
	\par
	\vspace{1em}
}

\sectionfont{\fontsize{12}{12}\bfseries}
\subsectionfont{\fontsize{10}{12}\normalfont}
\subsubsectionfont{\fontsize{10}{12}\normalfont}

\begin{document}

\maketitle
\pagestyle{fancy}

\fi

\begin{itemize}
	\item Verification can be done with static analysis and/or dynamic testing.
	\begin{itemize}
		\item \emph{Aside: Sounds more like validation to me but idk.}
	\end{itemize}
	\item It is unlikely dynamic testing can identify all possible faults.
	\begin{itemize}
		\item Some faults are incredibly difficult to trigger.
	\end{itemize}
	\item All automated software verification techniques (such as static analysis) can be categorized as:
	\begin{enumerate}
		\item Sound.
		\begin{itemize}
			\item Only accepts systems that don't do some particular thing.
			\begin{itemize}
				\item I.E. No false negatives.
			\end{itemize}
		\end{itemize}
		\item Complete.
		\begin{itemize}
			\item Only accepts systems that do some particular thing.
			\begin{itemize}
				\item I.E. No false positives.
			\end{itemize}
		\end{itemize}
		\item Decidable.
		\begin{itemize}
			\item Only accepts correct systems (and terminates).
		\end{itemize}
	\end{enumerate}
	\item All automated verification techniques are incomplete and/or unsound and/or undecidable.
	\item Many important properties of a system cannot be decided.
	\begin{itemize}
		\item So, said property of a system cannot be guaranteed after verification.
		\item Many other properties, however, can be decided.
		\begin{itemize}
			\item Or, the approximations of the property may be decidable.
		\end{itemize}
	\end{itemize}
	\item Compilers are the most common static analyzer software engineers interact with.
	\begin{itemize}
		\item Type checking is an important, decidable property that compilers are able to verify.
	\end{itemize}
	
\end{itemize}

\ifdefined\iscombined
	\newpage
\else
	\end{document}
\fi
