\ifdefined\iscombined
	\lecturetitle{Factors in Testing}
\else
\documentclass{article}
\usepackage{changepage}
\usepackage{centernot}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{braket}
\usepackage{comment}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{backgrounds, calc, positioning}

\date{
	\vspace{-.75em}
	{\large \today}
}

\title{
	\vspace*{-1.5em}
	{\Huge Lecture 25} \\
	\vspace{-1em}
	\rule{\textwidth/4}{.01em} \\
	\vspace{-.25em}
	{\Large Factors in Testing}
	\vspace{-.75em}
}

\author{
	{\large Matthew Farah}
}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
	citecolor=blue,
	anchorcolor=blue
}

\fancyhead{}
\fancyhead[L]{\today}
\fancyhead[R]{Lecture 25 - Factors in Testing}

\setlength{\parindent}{0cm}

\lstset{
	basicstyle=\ttfamily\small,
	frame=single,
	tabsize=4,
	breaklines=true,
	numbers=left,
	numberstyle=\tiny,
	numbersep=8pt,
	xleftmargin=1.5em,
	framexleftmargin=1.5em
}

\newcounter{example}
\renewcommand{\theexample}{\arabic{example}}

\newenvironment{example}[1][]{
	\refstepcounter{example}
	\begin{adjustwidth}{1.5em}{}
	\noindent\textbf{\ifx&#1&Example \theexample:\else Example \theexample \ (#1):\fi}
	\ignorespaces
}{
	\vspace{.5em}
	\end{adjustwidth}
}

\newcounter{subexample}
\renewcommand{\thesubexample}{\alph{subexample}}

\newenvironment{subexample}{
	\setcounter{step}{0}
	\refstepcounter{subexample}
	\vspace{1em}\par\noindent
	\begin{adjustwidth}{1.5em}{}
	\noindent\textbf{(\thesubexample)}
	\ignorespaces
}{
	\par
	\vspace{1em}
	\end{adjustwidth}
}

\newenvironment{solution}{
	\vspace{.5em}
	\par
	\begin{adjustwidth}{1.5em}{}
	\textbf{{Solution:}}
	\par
	\vspace{.5em}
}{
	\vspace{1em}
	\end{adjustwidth}
}

\newcounter{step}
\renewcommand{\thestep}{\Roman{step}}

\newenvironment{step}{
	\refstepcounter{step}
	\vspace{1em}\par\noindent
	\ignorespaces\noindent\textbf{(\thestep)}
	\ignorespaces
}{
	\par
	\vspace{1em}
}

\sectionfont{\fontsize{12}{12}\bfseries}
\subsectionfont{\fontsize{10}{12}\normalfont}
\subsubsectionfont{\fontsize{10}{12}\normalfont}

\begin{document}

\maketitle
\pagestyle{fancy}

\fi

\begin{itemize}
	\item Test factors describe the quality-related attributes of a system.
	\begin{itemize}
		\item For example:
		\begin{itemize}
			\item Correctness.
			\item Data integrity.
			\item Ease of use.
			\begin{itemize}
				\item How user-friendly the system is for the client/clients.
			\end{itemize}
			\item Ease of operation.
			\begin{itemize}
				\item How easy the system is to develop, operate, maintain.
			\end{itemize}
		\end{itemize}
	\end{itemize}
	\item Test factors should:
	\begin{itemize}
		\item By decided by the client's/clients' requirements.
		\item Should consider all potential risks to the system.
	\end{itemize}
	\item The testing strategy for a system should be chosen according to:
	\begin{itemize}
		\item The team's past project experience.
		\item The team's size.
		\item The team's structure.
		\item The application domain of the system.
	\end{itemize}
	\item A system's risks belong to at least one of five categories.
	\begin{enumerate}
		\item Functional.
		\begin{itemize}
			\item Would affect the behaviour of one or more features.
		\end{itemize}
		\item Performance/scalability.
		\begin{itemize}
			\item Self-explanitory.
		\end{itemize}
		\item Security.
		\begin{itemize}
			\item Would make the system vulnerable to something.
			\begin{itemize}
				\item Important to note, applies to the security of the \underline{system}, not of users.
			\end{itemize}
			\item For example:
			\begin{itemize}
				\item Data breach risks.
				\item Dependency risks.
			\end{itemize}
		\end{itemize}
		\item Usability.
		\begin{itemize}
			\item Would affect the system's ease of use.
		\end{itemize}
		\item Maintainability.
		\begin{itemize}
			\item Would affect the system's ease of operation.
		\end{itemize}
	\end{enumerate}
	%TODO: Elaborate and/or give examples.
	\item The risks to a system can be described in matrix form.
	\begin{itemize}
		\item \emph{Aside: Will describe better and/or with examples if I have time.}
	\end{itemize}
\end{itemize}

\ifdefined\iscombined
	\newpage
\else
	\end{document}
\fi
