\ifdefined\iscombined
	\lecturetitle{Test Suites}
\else
\documentclass{article}
\usepackage{listings}
\usepackage{amsthm}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{sectsty}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{mathtools}

\date{
	\vspace{-.75em}
	{\large \today}
}

\title{
	\vspace*{-1.5em}
	{\Huge Lecture 5} \\
	\vspace{-1em}
	\rule{\textwidth/4}{.01em} \\
	\vspace{-.25em}
	{\Large Test Suites}
	\vspace{-.75em}
}

\author{
	{\large Matthew Farah}
}

\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=blue,
	citecolor=blue,
	anchorcolor=blue
}

\fancyhead{}
\fancyhead[L]{\today}
\fancyhead[R]{Lecture 5 - Test Suites}

\sectionfont{\fontsize{12}{12}\bfseries}
\subsectionfont{\fontsize{10}{12}\normalfont}
\subsubsectionfont{\fontsize{10}{12}\normalfont}

\begin{document}

\maketitle
\pagestyle{fancy}

\fi

\begin{itemize}
	\item A test suite is a collection of tests for a program/system.
	\begin{itemize}
		\item `SUT' = `System Under Test'.
	\end{itemize}
	\item There exist two kinds of unit tests:
	\begin{enumerate}
		\item Solitary.
		\begin{itemize}
			\item Isolates unit tests by using `test doubles' to simulate its dependencies.
		\end{itemize}
		\item Social.
		\begin{itemize}
			\item Any unit test that isn't solitary.
		\end{itemize}
	\end{enumerate}
	\item There are five important kinds of test doubles:
	\begin{enumerate}
		\item Dummies.
		\begin{itemize}
			\item Uses empty objects to simulate what dependencies return to the unit.
		\end{itemize}
		\item Fakes.
		\begin{itemize}
			\item Uses minimally functioning objects to simulate what dependencies return to the unit.
		\end{itemize}
		\item Stubs.
		\begin{itemize}
			\item Uses a static, pre-determined values to simulate what dependencies return to the unit.
		\end{itemize}
		\item Spies.
		\begin{itemize}
			\item Stubs that additionally record what the unit does with the value returned to it.
		\end{itemize}
		\item Mocks
		\begin{itemize}
			\item A minimal implementation of the dependency the unit relies on.
		\end{itemize}
	\end{enumerate}
	\item The type of test double to be used depends on both the unit itself and the bugs being tested for.
	\item Automated testing helps ensure system-breaking dependency changes are identified.
	\item Testing should always be done as early and often as possible.
	\begin{itemize}
		\item This minimizes the cost and time required to identify and fix bugs.
	\end{itemize}
\end{itemize}

\ifdefined\iscombined
	\newpage
\else
	\end{document}
\fi
